---
name: Okancan
surname: Balcı
address: "Ankara/ Turkey"
phone: +90 505 807 30 29
www: soon-to-be-filled
email: "okancan.balci@gmail.com"
github: Okancan-Balci
linkedin: okancan-balci
aboutme: "Aspiring Data Scientist"
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


# Education

```{r}
read.csv(file = "education.csv", header = TRUE) %>% 
  detailed_entries(
    what = degree,
    when = when,
    where = department,
    with = university,
    why = gpa
  )
```

# Technical Stack

## R Programming Language

* Base R, Tidyverse, ggplot2, Tidytext, Tidymodels, data.table

## Python

* NumPy, Pandas, Matplotlib, Seaborn, Sci-Kit Learn, Tensorflow, Selenium Webdriver

## SQL

* MySQL, Google BigQuery

## Statistics

* Linear Regression, Logistic Regression, Poisson Regression, A/B Test

## Misc

* Data Visualization, Data Wrangling, Data Cleaning, Web Scrapping, Natural Language Processing

# Certificates

# Academic Works

# Personal Projects





